Causal Compatibility Inequalities Admitting of Quantum Violations in the Triangle Structure

### 2017-05-30 documents/TriangleScenarioArXiv/ts.tex
Attempting sharelatex fix
Added Miguel insight for the second refinement to Fritz's Problem

    \section{Conclusions}
    \label{sec:conclusions}
    In \cref{sec:triangle_structure}, we elucidated that compatibility in the Triangle structure has been an unsolved problem for nearly a decade. Initially,~\citet{Branciard_2012} identified the Triangle structure as a challenging causal structure for studying non-classicality. Afterwards,~\citet{Henson_2014} were able to to classify the Triangle structure as \textit{interesting} which partially explains why it remains an enigma. Recently,~\citet{Fritz_2012} discovered the Fritz distribution as the first example of quantum non-classicality in the Triangle structure. Heretofore, researchers have been able to derive causal incompatibility inequalities~\cite{Inflation,Steudel_2010,Henson_2014} but unable to show that any are non-trivial in the context of quantum non-classicality. In \cref{sec:fritz_distribution} the Fritz distribution was described in detail along with Fritz's Problem~\cite[Problem 2.17]{Fritz_2012}.

@@

    In consideration of out resolution to \ref{r:1}, we additionally propose two more refinements to Fritz's Problem that are concerned more with the nature of the entanglement resource being exploited in a incompatible quantum distribution:
    \begin{enumerate}[label=\textbf{R.\arabic*}]
        \setcounter{enumi}{1}
        \item \label{r:2} Find incompatible quantum distributions on the Triangle structure that require entanglement in more than one shared state.
        \item \label{r:3} Find incompatible quantum distributions on the Triangle structure that satisfy all Bell structure inequalities under Fritz-type embeddings.
    \end{enumerate}

    Fritz's Problem is concerned with identifying incompatible quantum distributions in the Triangle structure that are qualitatively different than the non-classical distributions of the Bell structure discussed in \cref{sec:bell_structure}. When specifically concerned with entanglement resources, Bell structure non-classicality exploits the entanglement of a single bipartite quantum state. In the Triangle structure, the observable nodes $A,B,C$ have access to potentially three different bipartite quantum states. As noted in \cref{sec:fritz_distribution}, the Fritz distribution can be implemented using only a single entangled state\footnote{Of course there exists implementations that make use of three entangled states but at minimum only one is necessary.}. The question, as proposed by \ref{r:2}, remains: does there exist incompatible quantum distributions that genuinely require the entanglement resources of three states? Finding such distributions would affirmatively demonstrate a new form of entanglement resource distinct to the Triangle structure. Moreover \ref{r:3} is justified as a valid interpretation of Fritz's Problem in the following sense: the Fritz distribution was constructed by embedding a quantum distribution incompatible with the Bell structure (\cref{fig:bell_scenario}) into the Triangle structure via the re-imagined version of the Triangle scenario (\cref{fig:triangle_structure_with_fritz_bell_embedded}). Furthermore, the logic of \cref{sec:fritz_distribution} shows that \textit{any} Bell structure compatibility inequality can be upgraded to a compatibility inequality for the Triangle structure, provided one restricts the domain of those inequalities to distributions possessing appropriate perfect correlations. Suppose one relaxed that restriction, then it becomes qualitatively reasonable to associate incompatibility via violations of upgraded inequalities with the same variety of incompatibility that is familiar in the Bell structure. Therefore, satisfying all such upgraded inequalities is a sufficient condition for a new type of incompatibility that is genuinely distinct from Bell structure incompatibility. In summary, it remains unclear whether or not \ref{r:2} or \ref{r:3} is a harder problem or if either is even feasible.

@@

    \setlength{\bibsep}{3pt plus 3pt minus 2pt}
    \bibliographystyle{apsrev4-1}
    \nocite{apsrev41Control}
    \bibliography{references}

>>>>

    \section{Conclusions}
    \label{sec:conclusions}
    In \cref{sec:triangle_structure}, we elucidated that compatibility in the Triangle structure has been an unsolved problem for nearly a decade. Initially,~\citet{Branciard_2012} identified the Triangle structure as a challenging causal structure for studying non-classicality. Afterwards,~\citet{Henson_2014} were able to to classify the Triangle structure as \textit{interesting} which partially explains why it remains an enigma. Recently,~\citet{Fritz_2012} discovered the Fritz distribution as the first example of quantum non-classicality in the Triangle structure. In \cref{sec:fritz_distribution} the Fritz distribution was described in detail along with Fritz's Problem~\cite[Problem 2.17]{Fritz_2012}. Heretofore, researchers have been able to derive causal incompatibility inequalities~\cite{Inflation,Steudel_2010,Henson_2014} but unable to show that any are non-trivial in the context of quantum non-classicality.

@@

    In consideration of our resolution to \ref{r:1}, we additionally propose two more refinements to Fritz's Problem that are concerned more with the nature of the entanglement resource being exploited in a incompatible quantum distribution:
    \begin{enumerate}[label=\textbf{R.\arabic*}]
        \setcounter{enumi}{1}
        \item \label{r:2} Find incompatible quantum distributions on the Triangle structure that require entanglement in more than one shared state.
        \item \label{r:3} Find incompatible quantum distributions on the Triangle structure that satisfy all Bell structure inequalities under Fritz-type embeddings.
    \end{enumerate}

    Fritz's Problem is concerned with identifying incompatible quantum distributions in the Triangle structure that are qualitatively different than the non-classical distributions of the Bell structure discussed in \cref{sec:bell_structure}. When specifically concerned with entanglement resources, Bell structure non-classicality exploits the entanglement of a single bipartite quantum state. In the Triangle structure, the observable nodes $A,B,C$ have access to potentially three different bipartite quantum states. As noted in \cref{sec:fritz_distribution}, the Fritz distribution can be implemented using only a single entangled state\footnote{Of course there exists implementations that make use of three entangled states but at minimum only one is necessary.}. The question, as proposed by \ref{r:2}, remains: does there exist incompatible quantum distributions that genuinely require the entanglement resources of three states? At first, one might suspect that finding such distributions would affirmatively demonstrate a new form of entanglement resource distinct to the Triangle structure. Unfortunately, this is simply not the case. By increasing the cardinality of the outcomes for $A, B, C$, it is possible to generate a distribution that is non-classical yet quantum and requires all three of the shared resources to be entangled. This can be accomplished by superimposing three copies of statistically independent Fritz distributions to the Triangle Structure, each of which utilizes a distinct party to announce the corresponding measurement pseudo-settings. Such a distribution would be of the form described by \ref{r:2} because under this construction, the removal of any entangled resource would render the distribution quantum-inaccessible.\footnote{This insight was originally made by Miguel Navascués in private communications.} Consequently, it becomes desirable to find non-classical quantum correlations for the Triangle Structure which have the fewest number of outcomes.

    Moreover \ref{r:3} is justified as a valid interpretation of Fritz's Problem in the following sense: the Fritz distribution was constructed by embedding a quantum distribution incompatible with the Bell structure (\cref{fig:bell_scenario}) into the Triangle structure via the re-imagined version of the Triangle scenario (\cref{fig:triangle_structure_with_fritz_bell_embedded}). Furthermore, the logic of \cref{sec:fritz_distribution} shows that \textit{any} Bell structure compatibility inequality can be upgraded to a compatibility inequality for the Triangle structure, provided one restricts the domain of those inequalities to distributions possessing appropriate perfect correlations. Suppose one relaxed that restriction, then it becomes qualitatively reasonable to associate incompatibility via violations of upgraded inequalities with the same variety of incompatibility that is familiar in the Bell structure. Therefore, satisfying all such upgraded inequalities is a sufficient condition for a new type of incompatibility that is genuinely distinct from Bell structure incompatibility. Ultimately, it remains unclear whether or not a positive resolution to \ref{r:3} is even feasible.

@@

    \setlength{\bibsep}{3pt plus 3pt minus 2pt}
    \bibliographystyle{apsrev4-1}
    % \nocite{apsrev41Control}
    \bibliography{references}
